2.3 Prob Model for PCR Positivity Estimation

### 2024-04-05 2_scripts/2.2.a CBS Preprocessing and Fig.qmd
minor changes, need to work on plot part later

p01<-CBS_melt %>%
  ggplot(aes(x=samplemonth, y=prop, group=Adj, colour=Adj)) +
  geom_point(aes(colour=Adj)) +
#  geom_smooth(method = "loess", aes(colour=Adj), se=FALSE) +
  geom_line(aes(colour=Adj))  + #non-smooth curve
  theme_bw()

>>>>

p01<-CBS_melt %>%
  ggplot(aes(x=samplemonth, y=prop, group=Adj, colour=Adj)) +
  geom_point(aes(colour=Adj)) +
# geom_smooth(method = "loess", aes(colour=Adj), se=FALSE) +
  geom_line(aes(colour=Adj))  + # non-smooth curve
  theme_bw()

### 2024-04-05 2_scripts/2.3 Prob Model for PCR pos.qmd
minor changes, need to work on plot part later

```{r}
# The linear model using log_e transformed abbott_n and roche_n

@@

#### Apply the model lm01 to the CBS data
```{r}
log_abbott_n<-predict(lm01, newdata = CBSs, "response")
summary(log_abbott_n)

@@

#### plot: sero-prevalence, using predicted Abbott positivity
```{r}
tb_abb<-CBSs %>%
  group_by(samplemonth, region) %>%
  summarise(n = n() , 
            pos_abbott= sum(pos_abbott, na.rm = T), 
            pos_roche= sum(pos_roche, na.rm = T)
            )
tb_abb$prop.abbott<-tb_abb$pos_abbott/tb_abb$n
tb_abb$prop.roche<-tb_abb$pos_roche/tb_abb$n

>>>>

#### 3.1 The linear (log) model
```{r}
# The linear model using log_e transformed abbott_n and roche_n

@@

#### 3.2 Apply the model lm01 to the CBS data
```{r}
log_abbott_n<-predict(lm01, newdata = CBSs, "response")
summary(log_abbott_n)

@@

#### 3.3 plot: sero-prevalence, using predicted Abbott positivity
```{r}
tb_abb<-CBSs %>%
  group_by(samplemonth, region) %>%
  summarise(n = n() , 
            pos_abbott= sum(pos_abbott, na.rm = T), 
            pos_roche= sum(pos_roche, na.rm = T)
            )
tb_abb$prop.abbott<-tb_abb$pos_abbott/tb_abb$n
tb_abb$prop.roche<-tb_abb$pos_roche/tb_abb$n
